---
title: "Wed_Inclass"
author: "Esteffani Maldonado"
date: "11/17/2021"
output: html_document
---

# This is a quick-turn challenge.  It relates to Question 2 of Quiz 8 in our course. Take a look at that quiz question and then.

## The researchers wanted to know if the spiders could run faster, on average, without the hindrance of a pedipalp

### Finish this writeUp and knit the result to a pdf file.  


### Then add this to your github account and turn it in by emailing me the link to it in your github account,



```{r, message=FALSE}
require(tidyverse)
require(tigerstats)
require(abd)
data("SpiderSpeed")
```

```{r, eval=TRUE}
#mydata <- gather(SpiderSpeed, variable, value) 
dat <- gather(SpiderSpeed, BorA, speed)
```

```{r}
boxplot(speed~BorA,data = dat , main = "Speed_BorA")
```
  
In the boxplot, we can see that the speed.after is higher compared to speed.before, indicating that the speed of the spiders had increased after they had their pedipalps removed.
  
# Numerical Results
  
```{r}
favstats(speed~BorA,data=dat)
```  
   
The mean speed of the spiders after having their pedipalps removed increased from the mean before. The mean for after is about 3.85, and the speed for before was 2.67.
 
 
# Inferential Results

```{r}
t.test(speed~BorA,data=dat)
```
  
From the t-test, we can see that the p-value is 0.0004611. This is a very small value, meaning that there is definitely a difference in the speed of the spiders before their pedipalps were removed and the speed of the spiders after they were removed. The 95% confidence interval is about 0.578 to 1.793. 
  

